---
title: "Week 1, Assignment 1B"
author: "Lukas Moser"
format: html
editor: visual
---

# Exercise: Week 1, Part B:

## Exercise:

Create an HTML document with R code that samples 100 values from a negative binomial distribution (say, mu=10, dispersion=2; using the parameterisation with mean=mu and variance=mu+mu2\*dispersion); create a histogram of sampled data on both the linear and log \[or maybe log(x+1) due to zeros\] scale; Write 1-2 sentences to describe your steps (ideally also with section headings) and report the mean and variance of the sample in line in the text.

## Create the samples distribution

First write down all the given parameters:

```{r}
size <- 100
mu <- 10
dispersion <- 2
mean <- mu
variance <- mu+mu^2*dispersion
```

In a next step create the sampling:

As I am not very familiar with this notation of a negative binominal distribution, I checked [here](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/NegBinomial.html) for a better understanding. It states: "An alternative parametrization (often used in ecology) is by the mean mu (see above), and size, the dispersion parameter, where prob = size/(size+mu). The variance is mu + mu\^2/size in this parametrization."


**What confuses me a little bit is that everywhere variance is defined as: mu + mu\^2/dispersion, however in the exercise it is defined as mu+mu\^2\*dispersion, which looks somehow weird to me.**

```{r}
x1 <- rnbinom(100, mu = 10, size = 2)
```

Now we can make the linear histogram:

```{r}
h1 <- hist(x1, breaks = 20, xlab= "random variable", 
           main= "Negative Binominal Distribution (linear)")
```

Now we can do the same on a log scale:

```{r}
hist1_log = log10(h1$counts)
hist.data = hist(x1, breaks = 20, plot = FALSE )
hist.data$counts = log10(hist.data$counts+1)
plot(hist.data, ylab='log10(Frequency+1)', 
     xlab= "random variable", 
     main= "Negative Binominal Distribution (log10(x+1))", 
     col = "lightgrey")

```

Next we will get the mean and variance of the sample:

```{r}
mean_sample = mean(x1)
variance_sample = var(x1)
```

The mean of the sample is `r mean_sample` and the variance of the sample is `r variance_sample`.


